\input{Project/preamble}
\input{Project/format}


\title{PS1 - Devin}



\begin{document}
\vspace*{-30mm}
\raggedright
\begin{Large}
    \textsf{\textbf{Problem Set One - Jan 23rd}}
    
        Devin Williams
\end{Large}

\begin{tcolorbox}[
    title={My Interests in Economics and Data Science},
    colback=white,
    colframe=black,
]
    

\setlength{\parindent}{20pt} % sets indentation for paragraphs within tcolorbox
\doublespacing % allowed the document to be double spaced.

In general, I have a variety of different interests in the world of data science. My main goal within my academic career is to be able to use data to answer questions related to sport business issues. Including analyzing public subsidies for professional sports facilities. This is also a sport economics question, so being able to understand how to use data science to answer questions within sports economics is a strong interest for me within my academic career. 

I wanted to take this class to better understand all of the tools available to me when looking at future research topics in economics and data science. Being able to understand all the ways that I can make my life easier throughout my academic and professional career will continue to be more important. I hope I can apply many of these data analysis and AI tools to the final project in this class as well, although I am not sure what I will be doing it about. 

On a personal level,  I am hoping that after graduation I will be able to work in a data analyst role for a professional sports team. Whether that be related to business or athlete performance remains to be seen, but as much of my research topics within my Masters program relate more to the business side of sport, I hope that I will be able to research a topic that will allow me to transition to the professional world easily after graduation. 
\end{tcolorbox}

\begin{tcolorbox} [
    title={Equation},
    colback=white,
    colframe=black,
    top=0mm
]
    \[ a^2 + b^2 = c^2 \]
\end{tcolorbox}






\end{document}
