\documentclass[12pt,letterpaper]{article}
\usepackage[left=1.1in,top=0.8in,right=1.1in,bottom=0.9in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{fancyhdr}
\usepackage{booktabs}
%\usepackage{graphicx}
%\usepackage{ctex}
%\usepackage{braket}
%\usepackage{mathpazo}
%\usepackage{minted}
%\usepackage{xcolor} % to access the named colour LightGray
%\definecolor{LightGray}{gray}{0.9}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
%\usepackage{graphicx}
%\usepackage{background}
\usepackage{setspace}
\onehalfspacing
\pagestyle{fancy}
\fancyhf{}
\lhead{ECON5253}
\rhead{Spring 2025}
%\rhead{Chang Gao}
\cfoot{\thepage}
\begin{document}
	\begin{center}
	\noindent{\Large Problem Set 1}\medskip\\
	\end{center}
\noindent{\bf\large Brief Summary}\smallskip\\
My interest in economic research originates from my observations in residents' living standard change from time to time --- both rapid growth and sudden recession has been witnessed in my hometown China. It looks obvious that when the economy grows fast, people looks happy, and under the recession, most people are not happy. You can feel this if you take a train and look at others. Then I found most of my interested question are on macro-finance.

I take this class because I felt a little bit lost in economic research. At the beginning of PhD study, I thought macro models may help with understand what I observed. However, they are far from the real world, I cannot find a good bridge between the macro model in textbook and what I witnessed --- the real world is much more complicated. It is almost impossible for a model with many variables to be true.. So, I want to check out more empirical stuff, that is why I take this course. I cannot say a model is true, but the data can at least tell us some truth. I plan to develop data/econometric skills.

I will continue work on the China housing booming/collapse paper, Dr. Yang gave me very helpful suggestions last semester. I didn't have time to work on the data for preparing the Fall 2024 and Winter 2024 teaching. I wish to have some result by the end of this semester.

The plan after graduation: Ultimately (when I am old), I wish to return to home country and work as a professor who could help people know more about the truth in economy situation. Finding a research faculty position is very hard at the current situation, so I prefer research jobs in banking and finance sectors now, which comes with good income and matches the interest.\medskip\\
\noindent{\bf\large Equation}\smallskip\\

$$a^2+b^2=c^2$$
\end{document}